Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
properly reference Moon tile figure

Figure 2 shows the dramatic improvement achieved toward maintaining a 
consistent coadd background level by virtue of folding in NEOWISER data and 
applying the frame-level Moon rejection cut, for a tile with severe Moon 
contamination during the AllWISE phase.

>>>>

Figure \ref{fig:moon_3433p000} shows the dramatic improvement achieved toward 
maintaining a consistent coadd background level by virtue of folding in 
NEOWISER data and applying the frame-level Moon rejection cut, for a tile with 
severe Moon contamination during the AllWISE phase.
